Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-26 paper.qmd
Rearranged Figure 12

five_gau_proj_tsne_model1 + five_gau_proj_tsne_model2 +
  five_gau_proj_umap_model1 + five_gau_proj_umap_model2 +
  five_gau_proj_pacmap_model1 + five_gau_proj_pacmap_model2 +
  plot_layout(guides = "collect", ncol = 2) &
  theme(legend.position='none')
```

>>>>

five_gau_proj_tsne_model1 + five_gau_proj_umap_model1 + five_gau_proj_pacmap_model1 + five_gau_proj_tsne_model2 + five_gau_proj_umap_model2 + five_gau_proj_pacmap_model2 +
  plot_layout(guides = "collect", nrow = 2) &
  theme(legend.position='none')
```
